### 2016-09-07 notions.tex
Theorems comparing our definition to NY definition

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
\jnote{Note~$q$ is overloaded here.}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

\heading{Comparison to the Naor-Yogev definition.}
The structure of the Naor-Yogev definition is different from ours.
Lifting their definition\footnote{They focus specifically on set-representation data structures
with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
to extend their definition to more closely match ours.}
to our setting,
the experiment is similar but the attacker
succeeds only if it outputs a (single) query $q$ for which
$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
previously query $q$ to its $\TestOracle$ oracle}. We refer to
Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
We define the advantage of adversary~$A$ as
$\NYAdvCorrect{\Pi,\distr{}{}}{A} = \Prob{\NYExpCorrect{\Pi,\distr{}{}}{A}=1}$,
and write $\NYAdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,\epsilon')$-NY-correct if
$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon'$. \jnote{This should all probably
move to an appendix; it's a lot of notation to digest for something we never use again
in the paper.}

@@

\jnote{There's something ``morally wrong'' with the follow theorem statement:
if we increase $q$ then the assumption about the NY-correctness of $\Pi$ (presumably)
gets stronger---even if formally that is not true---but the conclusion of the theorem
becomes weaker.}

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon')$-NY-correct, then it is also
$(t, q', r, q'\epsilon'/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
and assume that for some $q' \leq q+1$ and $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries (note that without loss of generality
we may assume $A$ always makes exactly $q'$ queries) such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
With probability at least
$q'\epsilon'/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon'/r)=\epsilon'$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

\jnote{It is unclear whether the above is tight, but it is also unclear whether
that is something worth thinking about. }

\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors.
If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$.
It is unclear whether this is tight.

\item There is a contrived scheme that is $(t, q, 2, 0)$-correct but not NY-secure at all; the basic idea is
to have a set-representation that always has \emph{exactly one} false positive that is easy to find
given the public information.

\item If a scheme is $(t,q,1,\epsilon)$-correct, then it is also $\epsilon$-secure under the NY definition,
at least for attackers making at most $q-1$ queries.
This is immediate.
\end{enumerate}
\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
where finding the first false positive is hard but then the rest are easy; can have
a scheme where finding one false positive is easy but there do not exist
any more false positives.}

>>>>

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon$.
\jnote{Note~$q$ is overloaded here.}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

\heading{Comparison to the Naor-Yogev definition.}
The structure of the Naor-Yogev definition is different from ours.
Lifting their definition\footnote{They focus specifically on set-representation data structures
with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
to extend their definition to more closely match ours.}
to our setting,
the experiment is similar but the attacker
succeeds only if it outputs a (single) query $q$ for which
$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
previously query $q$ to its $\TestOracle$ oracle}. We refer to
Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
We define the advantage of adversary~$A$ as
$\NYAdvCorrect{\Pi,\distr{}{}}{A} = \Prob{\NYExpCorrect{\Pi,\distr{}{}}{A}=1}$,
and write $\NYAdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon$. \jnote{This should all probably
move to an appendix; it's a lot of notation to digest for something we never use again
in the paper.}

@@

\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
is ``better'' than the definition in Figure~\ref{fig:NYcorrectness}?}

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon)$-NY-correct,
and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
some $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon/r$.
(Note that
we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
With probability at least
$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon/r)=\epsilon$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

\jnote{The above is tight, at least for $r=1$. Specifically, consider a scheme
in which every query is independently
answered incorrectly with probability~$\epsilon$. Such a
scheme will be $(t,q,\epsilon)$-NY-correct
for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
under our correctness definition (for $r=1$).}

\begin{theorem}
If $\Pi$ is $(t, q, 1, \epsilon)$-correct, then it is also $(t, q-1, \epsilon)$-NY-correct.
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,1,\epsilon)$-correct,
and assume that for some distribution $\distr{}{}$
there is an adversary $A$ running in time~$t$
and making at most $q-1$ oracle queries such that
$\NYAdvCorrect{\Pi,\distr{}{}}{A} > \epsilon$.
Let $A'$ be the algorithm that simply
runs~$A$, passing the oracle queries of $A$ to its own oracle, until $A$ terminates
with output~$q$; then, $A'$ sends $q$ to $\TestOracle$. \jnote{$q$ is (still)
overloaded!} It is immediate that $A'$ makes at most $q$ oracle queries, and
$\AdvCorrect{\Pi,\distr{}{},1}{A'} \geq \NYAdvCorrect{\Pi,\distr{}{}}{A}$, a contradiction.
\end{proof}

\begin{theorem}
There exists a set-representation data structure $\Pi$ that
is $(t, q, 2, 0)$-correct, but is not $(t, 0, \epsilon)$-NY-correct
for any $\epsilon<1$.
\end{theorem}
\begin{proof}
We prove the theorem for set-membership data structures.
Let $x \in {\cal X}$ be an arbitrary element of the universe, and
let $\Pi$ be the data structure in which $\Rep(S)$ outputs $\pubaux=\privaux=S$, and
$\Qry(S, S, q_y)$ outputs $q_y(S)$ if $y \neq x$ but outputs $1-q_x(S)$ otherwise. This
scheme always answers incorrectly for a single, fixed query, and answers
correctly for every other query. The theorem follows.
\end{proof}

\jnote{I'm not sure what to conclude from any of the results above. The proofs
are also all trivial.}

\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
where finding the first false positive is hard but then the rest are easy; can have
a scheme where finding one false positive is easy finding more is hard (e.g.,
because there do not exist
any more).}
